\documentclass{rkim-resume}

\name{Russell Kim}
\email{russellkim98@gmail.com}
\phone{(+1) 609-356-8385}
\github{russellkim98}
\linkedin{russellkim98}

\usepackage{CormorantGaramond}

\begin{document}

\maketitle%

\section{Professional \\ Experience}

\subsection{NLMatics}[New York, NY]
\begin{positions}
  \entry{NLP Research Intern}{Feb 2020~--~May 2020}
\end{positions}

\begin{itemize}
  \item Used principles from classic NLP, graph theory, bayesian probabilistic inference, bioinformatics, active learning, reinforcement learning and deep learning to create text sentiment analysis tools on large amounts of text data.
  \item Developed core API calls that implement an abstractive text summarizer based on a neural sequence to sequence model
  \item Worked with research training datasets such as GLUE and create self labeled datasets from publicly available corpuses based on in-house written algorithms such as siamese neural networks and deep Q-Learning.
\end{itemize}

\subsection{Princeton University}[Princeton, NJ]
\begin{positions}
  \entry{Undergraduate Research Fellow/ Keller Center}{Feb 2019~--~Sept 2019}
\end{positions}

\begin{itemize}
  \item Advisor: Prof.~Frederick Wherry (\href{https://sociology.princeton.edu/people/frederick-wherry}{https://sociology.princeton.edu/people/frederick-wherry})
  \item Time series analysis of credit card delinquencies based on financial data provided by the Brooklyn Financial Clinic and the Consumer Financial Protection Bureau.
  \item Implemented a web spider on Facebook\@ and created keyword network graph using a co-occurrence matrix to determine customer sentiment.
  \item Resulted in data contributed towards several research papers.
\end{itemize}

\subsection{Point72 Asset Management, LP}[New York, NY]
\begin{positions}
  \entry{Aperio Data Modeling Intern}{Jun 2018~--~Aug 2018}
\end{positions}

\begin{itemize}
  \item Worked under David Loaiza, PhD, on home construction company sales data and forecasting volatility trends
  \item Designed and implemented an automated script that would webscrape 12 different home construction websites periodically and store them in SQL databases.
  \item Developed an ARIMA time series forecasting the number of foreclosures and mortgage cancellations by exploring default trends and volatility in similar bunches of locations.
  \item Gave specific recomendations to change in project direction based on analysis over 8 years of home building data.
\end{itemize}

\subsection{CASTLE Labs at Princeton University}[Princeton, NJ]
\begin{positions}
  \entry{Undergraduate Research Intern}{Feb 2017~--~May 2018}
\end{positions}

\begin{itemize}
  \item Mentored by Prof. Warren Powell at the Computational Stochastic Optimization and Learning Lab at Princeton University
  \item Designed a testing environment for various reinforcement learning policies to trial competing policy classes in various environments 
  \item Simulated Google's AdWords system to exploit strengths of different policy classes in a second-price auction. Results and strategies were then implemented and used in a partnership with a hotel advertisement agency.
\end{itemize}

\section{Education}

\subsection{Princeton University}[Princeton, NJ]
\vspace{-\parskip}%
\begin{itemize}[label={}]
  \item B.S.E\ in ORFE with an emphasis on applied math and optimization\printdate{Sept 2016~--~Jun 2020}
  \item Thesis: {A Reinforcement Learning Based Approach to Pricing and Hedging Financial Derivatives}\href{https://github.com/russellkim98/Thesis/blob/master/Russell-Kim-Thesis.pdf}{\\(https://git.io/Jfrv7)}
  \item Advisor: Prof.~Mete Soner (\href{https://soner.princeton.edu/}{https://soner.princeton.edu/})
\end{itemize}
\section{Skills}


\begin{description}
  \item[Programming]: Python, Spark, SQL, UNIX, Matlab, \LaTeX, Bash, R, Java
  \item[Frameworks]: Tensorflow, Flask, PyTorch, OpenAI Gym, NLTK, spaCy, Keras, Gensim
  \item[Languages]: English, Korean, French
\end{description}


\section{Research \\ Interests}

Topics: Nonparametric reinforcement learning, stochastic systems under closed MC simulation, derivatives pricing, convexity in explainability AI.

\begin{itemize}
  \item Nonparametric discrete definition of financial derivatives.
  \item Confidence bounding in boundary decision problems with sparse input features.
  \item One-shot learning of complex objects using siamese neural networks.
\end{itemize}


\end{document}
